### 2009-05-19 doc/manuals/janitor/images/dependencies.tex
Temporary solution to save the nightlies - use old pgf style

\begin{tikzpicture}[>=latex,line join=bevel,]

@@

  \draw [->] (711bp,144bp) .. controls (710bp,136bp) and (710bp,127bp)  .. (710bp,108bp);

@@

  \draw [->] (732bp,221bp) .. controls (750bp,211bp) and (776bp,194bp)  .. (805bp,175bp);

@@

  \draw [->] (390bp,153bp) .. controls (417bp,143bp) and (463bp,125bp)  .. (501bp,108bp) .. controls (503bp,107bp) and (504bp,107bp)  .. (515bp,101bp);

@@

  \draw [->] (458bp,72bp) .. controls (458bp,64bp) and (458bp,55bp)  .. (458bp,36bp);

@@

  \draw [->] (727bp,147bp) .. controls (737bp,137bp) and (749bp,124bp)  .. (766bp,105bp);

@@

  \draw [->] (686bp,229bp) .. controls (625bp,216bp) and (472bp,184bp)  .. (392bp,167bp);

@@

  \draw [->] (341bp,155bp) .. controls (315bp,147bp) and (274bp,131bp)  .. (245bp,108bp) .. controls (224bp,90bp) and (207bp,65bp)  .. (192bp,36bp);

@@

  \draw [->] (685bp,231bp) .. controls (622bp,225bp) and (462bp,207bp)  .. (330bp,180bp) .. controls (214bp,155bp) and (185bp,147bp)  .. (73bp,108bp) .. controls (71bp,107bp) and (69bp,106bp)  .. (57bp,101bp);

@@

  \draw [->] (815bp,145bp) .. controls (810bp,137bp) and (803bp,126bp)  .. (792bp,107bp);

@@

  \draw [->] (739bp,232bp) .. controls (793bp,226bp) and (913bp,211bp)  .. (938bp,180bp) .. controls (953bp,160bp) and (938bp,132bp)  .. (917bp,105bp);

@@

  \draw [->] (724bp,217bp) .. controls (731bp,207bp) and (741bp,193bp)  .. (748bp,180bp) .. controls (758bp,160bp) and (767bp,135bp)  .. (776bp,108bp);

@@

  \draw [->] (339bp,159bp) .. controls (287bp,153bp) and (169bp,137bp)  .. (73bp,108bp) .. controls (71bp,107bp) and (68bp,106bp)  .. (56bp,102bp);

@@

  \draw [->] (392bp,156bp) .. controls (431bp,147bp) and (509bp,128bp)  .. (573bp,108bp) .. controls (576bp,107bp) and (579bp,106bp)  .. (592bp,102bp);

@@

  \draw [->] (736bp,153bp) .. controls (770bp,140bp) and (831bp,117bp)  .. (878bp,99bp);

@@

  \draw [->] (521bp,75bp) .. controls (509bp,65bp) and (494bp,51bp)  .. (474bp,33bp);

@@

  \draw [->] (151bp,72bp) .. controls (155bp,64bp) and (162bp,54bp)  .. (172bp,36bp);

@@

  \draw [->] (902bp,144bp) .. controls (902bp,136bp) and (902bp,127bp)  .. (902bp,108bp);

@@

  \draw [->] (697bp,219bp) .. controls (688bp,208bp) and (676bp,194bp)  .. (667bp,180bp) .. controls (654bp,160bp) and (642bp,135bp)  .. (630bp,108bp);

@@

  \draw [->] (349bp,148bp) .. controls (336bp,137bp) and (319bp,123bp)  .. (298bp,104bp);

@@

  \draw [->] (366bp,144bp) .. controls (366bp,136bp) and (366bp,127bp)  .. (366bp,108bp);

@@

  \draw [->] (712bp,216bp) .. controls (712bp,208bp) and (712bp,199bp)  .. (712bp,180bp);

@@

  \draw [->] (698bp,219bp) .. controls (690bp,208bp) and (680bp,194bp)  .. (676bp,180bp) .. controls (671bp,164bp) and (671bp,159bp)  .. (676bp,144bp) .. controls (679bp,134bp) and (684bp,123bp)  .. (695bp,106bp);

@@

  \draw [->] (781bp,72bp) .. controls (781bp,64bp) and (781bp,55bp)  .. (781bp,36bp);

@@

  \draw [->] (737bp,226bp) .. controls (767bp,217bp) and (821bp,199bp)  .. (866bp,180bp) .. controls (868bp,179bp) and (870bp,178bp)  .. (881bp,173bp);

@@

  \draw [->] (386bp,74bp) .. controls (399bp,63bp) and (418bp,49bp)  .. (440bp,32bp);

@@

  \draw [->] (384bp,148bp) .. controls (397bp,138bp) and (415bp,123bp)  .. (439bp,105bp);

@@

  \draw [->] (341bp,154bp) .. controls (306bp,142bp) and (238bp,121bp)  .. (181bp,103bp);

@@

  \draw (458bp,18bp) ellipse (27bp and 18bp);
  \draw (458bp,18bp) node {Note};

@@

  \draw (781bp,90bp) ellipse (27bp and 18bp);
  \draw (781bp,90bp) node {Execute};

@@

  \draw (281bp,90bp) ellipse (27bp and 18bp);
  \draw (281bp,90bp) node {Package};

@@

  \draw (623bp,90bp) ellipse (41bp and 18bp);
  \draw (623bp,90bp) node {DebianPackage};

@@

  \draw (902bp,90bp) ellipse (27bp and 18bp);
  \draw (902bp,90bp) node {Config};

@@

  \draw (183bp,18bp) ellipse (37bp and 18bp);
  \draw (183bp,18bp) node {MetaPackage};

@@

  \draw (366bp,90bp) ellipse (40bp and 18bp);
  \draw (366bp,90bp) node {NoteCollection};

@@

  \draw (709bp,90bp) ellipse (27bp and 18bp);
  \draw (709bp,90bp) node {Util};

@@

  \draw (366bp,162bp) ellipse (27bp and 18bp);
  \draw (366bp,162bp) node {Catalog};

@@

  \draw (537bp,90bp) ellipse (27bp and 18bp);
  \draw (537bp,90bp) node {Tag};

@@

  \draw (826bp,162bp) ellipse (31bp and 18bp);
  \draw (826bp,162bp) node {Filefetcher};

@@

  \draw (902bp,162bp) ellipse (27bp and 18bp);
  \draw (902bp,162bp) node {Common};

@@

  \draw (140bp,90bp) ellipse (58bp and 18bp);
  \draw (140bp,90bp) node {MetaPackageCollection};

@@

  \draw (712bp,162bp) ellipse (27bp and 18bp);
  \draw (712bp,162bp) node {Installer};

@@

  \draw (712bp,234bp) ellipse (27bp and 18bp);
  \draw (712bp,234bp) node {Janitor};

@@

  \draw (32bp,90bp) ellipse (32bp and 18bp);
  \draw (32bp,90bp) node {TarPackage};

@@

  \draw (458bp,90bp) ellipse (34bp and 18bp);
  \draw (458bp,90bp) node {BaseSystem};

@@

  \draw (781bp,18bp) ellipse (35bp and 18bp);
  \draw (781bp,18bp) node {InstallLogger};

>>>>

\begin{tikzpicture}[>=latex,join=bevel,]

@@

  \draw [->] (649bp,144bp) .. controls (648bp,136bp) and (648bp,127bp)  .. (647bp,108bp);

@@

  \draw [->] (670bp,221bp) .. controls (687bp,210bp) and (714bp,193bp)  .. (742bp,175bp);

@@

  \draw [->] (352bp,152bp) .. controls (376bp,141bp) and (416bp,124bp)  .. (449bp,108bp) .. controls (451bp,107bp) and (452bp,107bp)  .. (463bp,101bp);

@@

  \draw [->] (410bp,72bp) .. controls (410bp,64bp) and (410bp,55bp)  .. (410bp,36bp);

@@

  \draw [->] (665bp,146bp) .. controls (674bp,136bp) and (686bp,123bp)  .. (703bp,105bp);

@@

  \draw [->] (625bp,228bp) .. controls (568bp,216bp) and (430bp,184bp)  .. (355bp,168bp);

@@

  \draw [->] (304bp,155bp) .. controls (279bp,146bp) and (241bp,131bp)  .. (215bp,108bp) .. controls (195bp,90bp) and (180bp,65bp)  .. (166bp,36bp);

@@

  \draw [->] (624bp,231bp) .. controls (564bp,225bp) and (415bp,208bp)  .. (293bp,180bp) .. controls (191bp,156bp) and (166bp,146bp)  .. (67bp,108bp) .. controls (65bp,107bp) and (63bp,107bp)  .. (52bp,101bp);

@@

  \draw [->] (751bp,145bp) .. controls (746bp,137bp) and (739bp,126bp)  .. (728bp,107bp);

@@

  \draw [->] (678bp,231bp) .. controls (731bp,226bp) and (845bp,210bp)  .. (869bp,180bp) .. controls (884bp,160bp) and (869bp,132bp)  .. (848bp,105bp);

@@

  \draw [->] (663bp,218bp) .. controls (671bp,207bp) and (680bp,193bp)  .. (687bp,180bp) .. controls (696bp,160bp) and (704bp,136bp)  .. (712bp,108bp);

@@

  \draw [->] (302bp,159bp) .. controls (255bp,152bp) and (151bp,135bp)  .. (67bp,108bp) .. controls (65bp,107bp) and (63bp,106bp)  .. (51bp,102bp);

@@

  \draw [->] (355bp,156bp) .. controls (392bp,146bp) and (463bp,128bp)  .. (521bp,108bp) .. controls (523bp,107bp) and (526bp,106bp)  .. (538bp,102bp);

@@

  \draw [->] (674bp,153bp) .. controls (707bp,140bp) and (764bp,117bp)  .. (810bp,99bp);

@@

  \draw [->] (469bp,75bp) .. controls (458bp,65bp) and (444bp,51bp)  .. (425bp,33bp);

@@

  \draw [->] (131bp,72bp) .. controls (135bp,64bp) and (140bp,54bp)  .. (150bp,36bp);

@@

  \draw [->] (833bp,144bp) .. controls (833bp,136bp) and (833bp,127bp)  .. (833bp,108bp);

@@

  \draw [->] (636bp,219bp) .. controls (627bp,208bp) and (615bp,194bp)  .. (606bp,180bp) .. controls (593bp,160bp) and (582bp,135bp)  .. (571bp,108bp);

@@

  \draw [->] (313bp,147bp) .. controls (302bp,137bp) and (287bp,123bp)  .. (267bp,105bp);

@@

  \draw [->] (329bp,144bp) .. controls (329bp,136bp) and (329bp,127bp)  .. (329bp,108bp);

@@

  \draw [->] (651bp,216bp) .. controls (651bp,208bp) and (651bp,199bp)  .. (651bp,180bp);

@@

  \draw [->] (637bp,219bp) .. controls (629bp,208bp) and (619bp,194bp)  .. (615bp,180bp) .. controls (610bp,164bp) and (610bp,159bp)  .. (615bp,144bp) .. controls (617bp,134bp) and (622bp,124bp)  .. (633bp,106bp);

@@

  \draw [->] (717bp,72bp) .. controls (717bp,64bp) and (717bp,55bp)  .. (717bp,36bp);

@@

  \draw [->] (675bp,226bp) .. controls (704bp,216bp) and (755bp,198bp)  .. (797bp,180bp) .. controls (799bp,179bp) and (800bp,179bp)  .. (811bp,173bp);

@@

  \draw [->] (347bp,74bp) .. controls (358bp,64bp) and (373bp,51bp)  .. (393bp,33bp);

@@

  \draw [->] (345bp,147bp) .. controls (357bp,137bp) and (372bp,123bp)  .. (393bp,105bp);

@@

  \draw [->] (305bp,154bp) .. controls (271bp,142bp) and (208bp,120bp)  .. (156bp,102bp);

@@

  \draw (410bp,18bp) ellipse (27bp and 18bp);
  \draw (410bp,18bp) node {Note};

@@

  \draw (717bp,90bp) ellipse (27bp and 18bp);
  \draw (717bp,90bp) node {Execute};

@@

  \draw (251bp,90bp) ellipse (27bp and 18bp);
  \draw (251bp,90bp) node {Package};

@@

  \draw (565bp,90bp) ellipse (35bp and 18bp);
  \draw (565bp,90bp) node {DebianPackage};

@@

  \draw (833bp,90bp) ellipse (27bp and 18bp);
  \draw (833bp,90bp) node {Config};

@@

  \draw (159bp,18bp) ellipse (32bp and 18bp);
  \draw (159bp,18bp) node {MetaPackage};

@@

  \draw (329bp,90bp) ellipse (33bp and 18bp);
  \draw (329bp,90bp) node {NoteCollection};

@@

  \draw (645bp,90bp) ellipse (27bp and 18bp);
  \draw (645bp,90bp) node {Util};

@@

  \draw (329bp,162bp) ellipse (27bp and 18bp);
  \draw (329bp,162bp) node {Catalog};

@@

  \draw (485bp,90bp) ellipse (27bp and 18bp);
  \draw (485bp,90bp) node {Tag};

@@

  \draw (761bp,162bp) ellipse (27bp and 18bp);
  \draw (761bp,162bp) node {Filefetcher};

@@

  \draw (833bp,162bp) ellipse (27bp and 18bp);
  \draw (833bp,162bp) node {Common};

@@

  \draw (122bp,90bp) ellipse (46bp and 18bp);
  \draw (122bp,90bp) node {MetaPackageCollection};

@@

  \draw (651bp,162bp) ellipse (27bp and 18bp);
  \draw (651bp,162bp) node {Installer};

@@

  \draw (651bp,234bp) ellipse (27bp and 18bp);
  \draw (651bp,234bp) node {Janitor};

@@

  \draw (29bp,90bp) ellipse (29bp and 18bp);
  \draw (29bp,90bp) node {TarPackage};

@@

  \draw (410bp,90bp) ellipse (30bp and 18bp);
  \draw (410bp,90bp) node {BaseSystem};

@@

  \draw (717bp,18bp) ellipse (33bp and 18bp);
  \draw (717bp,18bp) node {InstallLogger};
